Behavior Driven Development in Haskell

### 2012-05-26 paper.tex
Add TBD to "Introduction"
Fix typo

\emph{IMPORTANT: @sol has to release a new version of hspec, that
includes the Spec-to-Specs and hspecX-to-hspec changes.  Otherwise the
code in this paper will not work!}

@@

>>>>

\emph{IMPORTANT: @sol has to release a new version of hspec, that
includes the Specs-to-Spec and hspecX-to-hspec changes.  Otherwise the
code in this paper will not work!}

@@

\begin{quote}
    TBD: Important points we want to say here:
    \begin{itemize}
        \item
            We use \doctest{} and \hspec{} to document behavior.
            (in contrast to other communities)
        \item
            Some features are missing from both, \doctest{} and
            \hspec{}.
        \item
            We extend them accordingly, and show how they can be used
            in combination to design, document and test Haskell code.
    \end{itemize}
\end{quote}
